%
%   Copyright 2013 Katarzyna Szawan <kat.szwn@gmail.com>
%       and Michał Rus <m@michalrus.com>
%
%   Licensed under the Apache License, Version 2.0 (the "License");
%   you may not use this file except in compliance with the License.
%   You may obtain a copy of the License at
%
%       http://www.apache.org/licenses/LICENSE-2.0
%
%   Unless required by applicable law or agreed to in writing, software
%   distributed under the License is distributed on an "AS IS" BASIS,
%   WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
%   See the License for the specific language governing permissions and
%   limitations under the License.
%

\subsection{Subtree recreation algorithm}
\label{subsec:subtree-recreation}

This algorithm has to be used on the server-side, when given a scenario in which:

\begin{enumerate}
	\item At least two users (Alice and Bob) share a map.
	\item The map gets synchronized on their devices in common state A.
	\item Alice goes offline.
	\item Bob, still online, deletes subtree S (changes state to B).
	\item Alice, still offline edits one of of children nodes in subtree S (changes state to B').
	\item Alice goes online and tries to synchronize.
	\item Server does not know a UUID of the children node, thus cannot naïvely merge B and B'.
	\item Now, subtree S has to be somehow recreated from Alice's version.
\end{enumerate}

The following steps then need to be taken:

\begin{enumerate}
	\item Akka, after receiving an update message and finding out that it does not know \emph{some} parents, responds with a request to resend the message, but, this time, with with full `genealogy' of the unknown parents.
	\item Android resends this update message at the same time adding a list of lists of parents up to the root node.
	\item Akka then knows where the lost subtrees were attached to and sends one more request for them.
	\item Android responds with original update message along with full requested subtrees from its local storage.
	\item Akka updates its DB and notifies all connected devices about the changes.
\end{enumerate}
